Meta-analysis

### 2020-06-23 04_MetaAnalysis.Rmd

Let's undertake the meta-analysis using the package `metafor`.
Ee are using the `spray_management` variable as a moderator and a interactive term to the `trial` random variable.
Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.

@@

AIC(PM_mv_St)
anova(PM_mv, PM_mv_St)
```

>>>>

Let's undertake the meta-analysis using the package `metafor`.
We are using the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.
Because we want to know the difference between all treatments and we have no reference treatment, we will remove the intercept.

@@

dat1$trial[1]

PM_mv_St1 <- rma.mv(
   yi = grain_SMD,
   vi, 
   mods = ~ spray_management,
   method = "ML",
   random = list(~ 1|location/year/trial_ref/dose/host_genotype/factor(row_spacing)/spray_management),
   data = dat1
)

AIC(PM_mv) # Printing the AIC of the model helps differentiate the models in the anova output
anova(PM_mv, PM_mv_St1) # PM_mv is the better model

```
